### 2022-02-17 doc/src/AdvPLIC.tex
Clarify requirements that AdvPLIC places on IMSICs.

If the interrupt domain's harts have IMSICs, the relevant interrupt
files of those IMSICs must support value \z{0x40000000} for register
\z{eidelivery}, else setting DM to zero (direct delivery mode) will
always have the same effect as setting IE to zero.
See Sections \ref{sec:IMSIC-reg-eidelivery}
and~\ref{sec:AdvPLIC-directMode-intrDelivery}.

>>>>

If DM is set to zero (direct delivery mode) and the interrupt domain's
harts have IMSICs then the relevant interrupt files of those IMSICs
must have \z{eidelivery} set to \z{0x40000000} for the interrupts to
be connected.
See Sections \ref{sec:IMSIC-reg-eidelivery}
and~\ref{sec:AdvPLIC-directMode-intrDelivery}.
